P4Query - an analyser framework for P4

### 2021-03-23 publications/The_tool_intro/paper.tex
tool_intro:adding github link
pub: conclusion

	The paper describes an analysis framework for P4. The framework makes possible development of different P4 related analysis methods in a generic and modular way. It uses an internal graph representation where the results of the methods are also represented as part of the graph (mainly by adding new edges to the graph). In this way the methods can use each other's results as well. The proposed tool makes also possible to create rapid, prototype implementation of different analysis concepts using a common toolset.

@@

	The goal of this paper is to introduce our static analysis framework for P4 programs, which uses a graph representation of the checked program. All of the analysers are based on the syntax tree of the examined P4 source and they extend it with new edges while creating new subgraphs -- like control-flow or call graph -- or new labels to store the calculated information.

>>>>

	The paper describes an analysis framework for P4~\footnote{The code is available from: \url{https://github.com/P4ELTE/P4Query}}. The framework makes possible development of different P4 related analysis methods in a generic and modular way. It uses an internal graph representation where the results of the methods are also represented as part of the graph (mainly by adding new edges to the graph). In this way the methods can use each other's results as well. The proposed tool makes also possible to create rapid, prototype implementation of different analysis concepts using a common toolset.

@@

	The framework uses a graph representation of the investigated program. All of the analysers are based on the syntax tree of the examined P4 source and they extend it with new edges while creating new subgraphs -- like control-flow or call graph -- or new labels to store the calculated information.
